---
title: "Built-in RStudio datasets"
author: "Marc Vila Forteza"
date: "5/13/2021"
output:
  ioslides_presentation: default
  slidy_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Coursera Developing data products Week 4 Assignment

This peer assessed assignment has two parts. First, you will create a Shiny application and deploy it on Rstudio's servers. Second, you will use Slidify or Rstudio Presenter to prepare a reproducible pitch presentation about your application.

**Your Shiny Application**
Write a shiny application with associated supporting documentation. The documentation should be thought of as whatever a user will need to get started using your application.

**Your Reproducible Pitch Presentation**
You get 5 slides (inclusive of the title slide)  to pitch a your app. You're going to create a web page using Slidify or Rstudio Presenter with an html5 slide deck.

## Built-in RStudio datasets App

### **Reproducible pitch**

This is an RStudio shiny application developed as a part of final project in the Developing Data Products course in Coursera Data Science Specialization.

### **The app is hosted at:**

[https://sinectica.shinyapps.io/Rdatasets/](https://sinectica.shinyapps.io/Rdatasets/)

### **The code can be found at:**

[https://github.com/sinectica/Rdatasets](https://github.com/sinectica/Rdatasets)

## Overview

The application returns the description, summary and the first n rows of any desired RStudio  built-in dataset, contained in the package "datasets".

**e.g.** This is summary of the dataset airquality:

```{r Summary, echo = FALSE}
summary(airquality)
```

## How the App works

Input (select) the Item of the desired dataset, among 106 different ones.
Input the number of rows that the user wants to be shown in the main panel.

The Output in the main panel will be:

- Title of the chosen dataset
- Summary of the dataset
- First n rows of the dataset




